---
title: "Bayesian regression"
author: "leechungpa"
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: yes
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: true
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), './docs/model.html')) })
---


# Packages and Reference

We use [BAS](https://cran.r-project.org/web/packages/BAS/BAS.pdf) packages. We proceeded with reference to [this example](https://cran.r-project.org/web/packages/BAS/vignettes/BAS-vignette.html).

Also, I give my sincere gratitude to [KKH](https://github.com/hun-learning94).



```{r, warning=FALSE, message=FALSE}
library(BAS)
library(tidyverse)
library(plotly)
```


# Preprocessing


```{r, echo=FALSE, warning=FALSE, message=FALSE}
original_data = read_csv("./data/df_R.csv")

set.seed(2020)
```


```{r}
colnames(original_data)
data = subset(original_data, select = -c(X1, idx)) 

data %>% head()
```



# murdPerPop

```{r}
y_name = 'murdPerPop'
```


## Model fit

```{r}
f = paste(y_name, " ~ . -murdPerPop -rapesPerPop -robbbPerPop -assaultPerPop -burglPerPop -larcPerPop -autoTheftPerPop -arsonsPerPop")

fit.gprior = bas.lm(f,
                    data = data,
                    method = "MCMC", # better than default "BAS"
                                     # for large p
                   prior = "ZS-null", # default
                                      # "JZS" also can use
                   modelprior = uniform(),
                   include.always = ~1,
                   MCMC.iterations = 100000)
```

```{r}
plot(fit.gprior, ask = F)
```

## model result


```{r}
summary(fit.gprior)
```

top 5 model

## Visualization of the Model Space

```{r}
image(fit.gprior, rotate=F)
```



## Posterior Distributions of Coefficients

```{r}
coef.gprior = coef(fit.gprior)
coef.gprior
```

### individual plot

probne0 > 0.2

```{r}
survivors = which(coef.gprior$probne0 > 0.2)
plot(coef.gprior, subset = survivors, ask = F)
```

### coefficient plot

```{r}
plot(confint(coef.gprior, parm = survivors))
```


## Prediction


```{r}
muhat.bma <- fitted(fit.gprior, estimator = "BMA")
bma <- predict(fit.gprior, estimator = "BMA", newdata = data)

result_data = original_data %>%
  mutate(pred_y=bma$fit)
```


```{r, echo=FALSE}
result_data %>%
  write_csv(paste('./data/pred_', y_name, '.csv', sep=''))
```


```{r, echo=FALSE}
a = round(min(result_data[[y_name]]))-1
b = round(max(result_data[[y_name]]))+1

x <- list(title = 'original', titlefont = f)
y <- list(title = 'predict', titlefont = f)

fig <- plot_ly(
  type = "scatter",
  x = result_data[[y_name]], 
  y = result_data[['pred_y']], 
  mode = "markers",  opacity=0.9,
  showlegend = FALSE) %>% 
  add_lines(x = a:b, y = a:b) %>%
  layout(xaxis = x, yaxis = y, title=y_name)
fig
```











# rapesPerPop

```{r}
y_name = 'rapesPerPop'
```


## Model fit

```{r}
f = paste(y_name, " ~ . -murdPerPop -rapesPerPop -robbbPerPop -assaultPerPop -burglPerPop -larcPerPop -autoTheftPerPop -arsonsPerPop")

fit.gprior = bas.lm(f,
                    data = data,
                    method = "MCMC", # better than default "BAS"
                                     # for large p
                   prior = "ZS-null", # default
                                      # "JZS" also can use
                   modelprior = uniform(),
                   include.always = ~1,
                   MCMC.iterations = 100000)
```

```{r}
plot(fit.gprior, ask = F)
```

## model result


```{r}
summary(fit.gprior)
```

top 5 model

## Visualization of the Model Space

```{r}
image(fit.gprior, rotate=F)
```



## Posterior Distributions of Coefficients

```{r}
coef.gprior = coef(fit.gprior)
coef.gprior
```

### individual plot

probne0 > 0.2

```{r}
survivors = which(coef.gprior$probne0 > 0.2)
plot(coef.gprior, subset = survivors, ask = F)
```

### coefficient plot

```{r}
plot(confint(coef.gprior, parm = survivors))
```


## Prediction


```{r}
muhat.bma <- fitted(fit.gprior, estimator = "BMA")
bma <- predict(fit.gprior, estimator = "BMA", newdata = data)

result_data = original_data %>%
  mutate(pred_y=bma$fit)
```


```{r, echo=FALSE}
result_data %>%
  write_csv(paste('./data/pred_', y_name, '.csv', sep=''))
```


```{r, echo=FALSE}
a = round(min(result_data[[y_name]],na.rm = TRUE))-1
b = round(max(result_data[[y_name]],na.rm = TRUE))+1

x <- list(title = 'original', titlefont = f)
y <- list(title = 'predict', titlefont = f)

fig <- plot_ly(
  type = "scatter",
  x = result_data[[y_name]], 
  y = result_data[['pred_y']], 
  mode = "markers",  opacity=0.9,
  showlegend = FALSE) %>% 
  add_lines(x = a:b, y = a:b) %>%
  layout(xaxis = x, yaxis = y, title=y_name)
fig
```













# robbbPerPop

```{r}
y_name = 'robbbPerPop'
```


## Model fit

```{r}
f = paste(y_name, " ~ . -murdPerPop -rapesPerPop -robbbPerPop -assaultPerPop -burglPerPop -larcPerPop -autoTheftPerPop -arsonsPerPop")

fit.gprior = bas.lm(f,
                    data = data,
                    method = "MCMC", # better than default "BAS"
                                     # for large p
                   prior = "ZS-null", # default
                                      # "JZS" also can use
                   modelprior = uniform(),
                   include.always = ~1,
                   MCMC.iterations = 100000)
```

```{r}
plot(fit.gprior, ask = F)
```

## model result


```{r}
summary(fit.gprior)
```

top 5 model

## Visualization of the Model Space

```{r}
image(fit.gprior, rotate=F)
```



## Posterior Distributions of Coefficients

```{r}
coef.gprior = coef(fit.gprior)
coef.gprior
```

### individual plot

probne0 > 0.2

```{r}
survivors = which(coef.gprior$probne0 > 0.2)
plot(coef.gprior, subset = survivors, ask = F)
```

### coefficient plot

```{r}
plot(confint(coef.gprior, parm = survivors))
```


## Prediction


```{r}
muhat.bma <- fitted(fit.gprior, estimator = "BMA")
bma <- predict(fit.gprior, estimator = "BMA", newdata = data)

result_data = original_data %>%
  mutate(pred_y=bma$fit)
```


```{r, echo=FALSE}
result_data %>%
  write_csv(paste('./data/pred_', y_name, '.csv', sep=''))
```


```{r, echo=FALSE}
a = round(min(result_data[[y_name]],na.rm = TRUE))-1
b = round(max(result_data[[y_name]],na.rm = TRUE))+1

x <- list(title = 'original', titlefont = f)
y <- list(title = 'predict', titlefont = f)

fig <- plot_ly(
  type = "scatter",
  x = result_data[[y_name]], 
  y = result_data[['pred_y']], 
  mode = "markers",  opacity=0.9,
  showlegend = FALSE) %>% 
  add_lines(x = a:b, y = a:b) %>%
  layout(xaxis = x, yaxis = y, title=y_name)
fig
```














# assaultPerPop

```{r}
y_name = 'assaultPerPop'
```


## Model fit

```{r}
f = paste(y_name, " ~ . -murdPerPop -rapesPerPop -robbbPerPop -assaultPerPop -burglPerPop -larcPerPop -autoTheftPerPop -arsonsPerPop")

fit.gprior = bas.lm(f,
                    data = data,
                    method = "MCMC", # better than default "BAS"
                                     # for large p
                   prior = "ZS-null", # default
                                      # "JZS" also can use
                   modelprior = uniform(),
                   include.always = ~1,
                   MCMC.iterations = 100000)
```

```{r}
plot(fit.gprior, ask = F)
```

## model result


```{r}
summary(fit.gprior)
```

top 5 model

## Visualization of the Model Space

```{r}
image(fit.gprior, rotate=F)
```



## Posterior Distributions of Coefficients

```{r}
coef.gprior = coef(fit.gprior)
coef.gprior
```

### individual plot

probne0 > 0.2

```{r}
survivors = which(coef.gprior$probne0 > 0.2)
plot(coef.gprior, subset = survivors, ask = F)
```

### coefficient plot

```{r}
plot(confint(coef.gprior, parm = survivors))
```


## Prediction


```{r}
muhat.bma <- fitted(fit.gprior, estimator = "BMA")
bma <- predict(fit.gprior, estimator = "BMA", newdata = data)

result_data = original_data %>%
  mutate(pred_y=bma$fit)
```


```{r, echo=FALSE}
result_data %>%
  write_csv(paste('./data/pred_', y_name, '.csv', sep=''))
```


```{r, echo=FALSE}
a = round(min(result_data[[y_name]],na.rm = TRUE))-1
b = round(max(result_data[[y_name]],na.rm = TRUE))+1

x <- list(title = 'original', titlefont = f)
y <- list(title = 'predict', titlefont = f)

fig <- plot_ly(
  type = "scatter",
  x = result_data[[y_name]], 
  y = result_data[['pred_y']], 
  mode = "markers",  opacity=0.9,
  showlegend = FALSE) %>% 
  add_lines(x = a:b, y = a:b) %>%
  layout(xaxis = x, yaxis = y, title=y_name)
fig
```









```{r, echo=FALSE, warning=FALSE, message=FALSE}
set.seed(2020)
```

# burglPerPop

```{r}
y_name = 'burglPerPop'
```


## Model fit

```{r}
f = paste(y_name, " ~ . -murdPerPop -rapesPerPop -robbbPerPop -assaultPerPop -burglPerPop -larcPerPop -autoTheftPerPop -arsonsPerPop")

fit.gprior = bas.lm(f,
                    data = data,
                    method = "MCMC", # better than default "BAS"
                                     # for large p
                   prior = "ZS-null", # default
                                      # "JZS" also can use
                   modelprior = uniform(),
                   include.always = ~1,
                   MCMC.iterations = 100000)
```

```{r}
plot(fit.gprior, ask = F)
```

## model result


```{r}
summary(fit.gprior)
```

top 5 model

## Visualization of the Model Space

```{r}
image(fit.gprior, rotate=F)
```



## Posterior Distributions of Coefficients

```{r}
coef.gprior = coef(fit.gprior)

coef.gprior
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
temp_11 = coef.gprior$namesx
temp_12 = coef.gprior$postmean
```

### individual plot

probne0 > 0.2

```{r}
survivors = which(coef.gprior$probne0 > 0.2)
plot(coef.gprior, subset = survivors, ask = F)
```

### coefficient plot

```{r}
plot(confint(coef.gprior, parm = survivors))
```


## Prediction


```{r}
muhat.bma <- fitted(fit.gprior, estimator = "BMA")
bma <- predict(fit.gprior, estimator = "BMA", newdata = data)

result_data = original_data %>%
  mutate(pred_y=bma$fit)
```


```{r, echo=FALSE}
result_data %>%
  write_csv(paste('./data/pred_', y_name, '.csv', sep=''))
```


```{r, echo=FALSE}
a = round(min(result_data[[y_name]],na.rm = TRUE))-1
b = round(max(result_data[[y_name]],na.rm = TRUE))+1

x <- list(title = 'original', titlefont = f)
y <- list(title = 'predict', titlefont = f)

fig <- plot_ly(
  type = "scatter",
  x = result_data[[y_name]], 
  y = result_data[['pred_y']], 
  mode = "markers",  opacity=0.9,
  showlegend = FALSE) %>% 
  add_lines(x = a:b, y = a:b) %>%
  layout(xaxis = x, yaxis = y, title=y_name)
fig
```













# larcPerPop

```{r}
y_name = 'larcPerPop'
```


## Model fit

```{r}
f = paste(y_name, " ~ . -murdPerPop -rapesPerPop -robbbPerPop -assaultPerPop -burglPerPop -larcPerPop -autoTheftPerPop -arsonsPerPop")

fit.gprior = bas.lm(f,
                    data = data,
                    method = "MCMC", # better than default "BAS"
                                     # for large p
                   prior = "ZS-null", # default
                                      # "JZS" also can use
                   modelprior = uniform(),
                   include.always = ~1,
                   MCMC.iterations = 100000)
```

```{r}
plot(fit.gprior, ask = F)
```

## model result


```{r}
summary(fit.gprior)
```

top 5 model

## Visualization of the Model Space

```{r}
image(fit.gprior, rotate=F)
```



## Posterior Distributions of Coefficients

```{r}
coef.gprior = coef(fit.gprior)
coef.gprior
```



```{r, echo=FALSE, warning=FALSE, message=FALSE}
tibble(index=temp_11, burglPerPop=temp_12, larcPerPop=coef.gprior$postmean) %>%
  write_csv('./data/coef.csv')
```



### individual plot

probne0 > 0.2

```{r}
survivors = which(coef.gprior$probne0 > 0.2)
plot(coef.gprior, subset = survivors, ask = F)
```

### coefficient plot

```{r}
plot(confint(coef.gprior, parm = survivors))
```


## Prediction


```{r}
muhat.bma <- fitted(fit.gprior, estimator = "BMA")
bma <- predict(fit.gprior, estimator = "BMA", newdata = data)

result_data = original_data %>%
  mutate(pred_y=bma$fit)
```


```{r, echo=FALSE}
result_data %>%
  write_csv(paste('./data/pred_', y_name, '.csv', sep=''))
```


```{r, echo=FALSE}
a = round(min(result_data[[y_name]],na.rm = TRUE))-1
b = round(max(result_data[[y_name]],na.rm = TRUE))+1

x <- list(title = 'original', titlefont = f)
y <- list(title = 'predict', titlefont = f)

fig <- plot_ly(
  type = "scatter",
  x = result_data[[y_name]], 
  y = result_data[['pred_y']], 
  mode = "markers",  opacity=0.9,
  showlegend = FALSE) %>% 
  add_lines(x = a:b, y = a:b) %>%
  layout(xaxis = x, yaxis = y, title=y_name)
fig
```







# autoTheftPerPop

```{r}
y_name = 'autoTheftPerPop'
```


## Model fit

```{r}
f = paste(y_name, " ~ . -murdPerPop -rapesPerPop -robbbPerPop -assaultPerPop -burglPerPop -larcPerPop -autoTheftPerPop -arsonsPerPop")

fit.gprior = bas.lm(f,
                    data = data,
                    method = "MCMC", # better than default "BAS"
                                     # for large p
                   prior = "ZS-null", # default
                                      # "JZS" also can use
                   modelprior = uniform(),
                   include.always = ~1,
                   MCMC.iterations = 100000)
```

```{r}
plot(fit.gprior, ask = F)
```

## model result


```{r}
summary(fit.gprior)
```

top 5 model

## Visualization of the Model Space

```{r}
image(fit.gprior, rotate=F)
```



## Posterior Distributions of Coefficients

```{r}
coef.gprior = coef(fit.gprior)
coef.gprior
```

### individual plot

probne0 > 0.2

```{r}
survivors = which(coef.gprior$probne0 > 0.2)
plot(coef.gprior, subset = survivors, ask = F)
```

### coefficient plot

```{r}
plot(confint(coef.gprior, parm = survivors))
```


## Prediction


```{r}
muhat.bma <- fitted(fit.gprior, estimator = "BMA")
bma <- predict(fit.gprior, estimator = "BMA", newdata = data)

result_data = original_data %>%
  mutate(pred_y=bma$fit)
```


```{r, echo=FALSE}
result_data %>%
  write_csv(paste('./data/pred_', y_name, '.csv', sep=''))
```


```{r, echo=FALSE}
a = round(min(result_data[[y_name]],na.rm = TRUE))-1
b = round(max(result_data[[y_name]],na.rm = TRUE))+1

x <- list(title = 'original', titlefont = f)
y <- list(title = 'predict', titlefont = f)

fig <- plot_ly(
  type = "scatter",
  x = result_data[[y_name]], 
  y = result_data[['pred_y']], 
  mode = "markers",  opacity=0.9,
  showlegend = FALSE) %>% 
  add_lines(x = a:b, y = a:b) %>%
  layout(xaxis = x, yaxis = y, title=y_name)
fig
```








# arsonsPerPop

```{r}
y_name = 'arsonsPerPop'
```


## Model fit

```{r}
f = paste(y_name, " ~ . -murdPerPop -rapesPerPop -robbbPerPop -assaultPerPop -burglPerPop -larcPerPop -autoTheftPerPop -arsonsPerPop")

fit.gprior = bas.lm(f,
                    data = data,
                    method = "MCMC", # better than default "BAS"
                                     # for large p
                   prior = "ZS-null", # default
                                      # "JZS" also can use
                   modelprior = uniform(),
                   include.always = ~1,
                   MCMC.iterations = 100000)
```

```{r}
plot(fit.gprior, ask = F)
```

## model result


```{r}
summary(fit.gprior)
```

top 5 model

## Visualization of the Model Space

```{r}
image(fit.gprior, rotate=F)
```



## Posterior Distributions of Coefficients

```{r}
coef.gprior = coef(fit.gprior)
coef.gprior
```

### individual plot

probne0 > 0.2

```{r}
survivors = which(coef.gprior$probne0 > 0.2)
plot(coef.gprior, subset = survivors, ask = F)
```

### coefficient plot

```{r}
plot(confint(coef.gprior, parm = survivors))
```


## Prediction


```{r}
muhat.bma <- fitted(fit.gprior, estimator = "BMA")
bma <- predict(fit.gprior, estimator = "BMA", newdata = data)

result_data = original_data %>%
  mutate(pred_y=bma$fit)
```


```{r, echo=FALSE}
result_data %>%
  write_csv(paste('./data/pred_', y_name, '.csv', sep=''))
```


```{r, echo=FALSE}
a = round(min(result_data[[y_name]],na.rm = TRUE))-1
b = round(max(result_data[[y_name]],na.rm = TRUE))+1


x <- list(title = 'original', titlefont = f)
y <- list(title = 'predict', titlefont = f)

fig <- plot_ly(
  type = "scatter",
  x = result_data[[y_name]], 
  y = result_data[['pred_y']], 
  mode = "markers",  opacity=0.9,
  showlegend = FALSE) %>% 
  add_lines(x = a:b, y = a:b) %>%
  layout(xaxis = x, yaxis = y, title=y_name)
fig
```






